% 4. Mechanical Model of Airways and Acini
\section{Mechanical Model of Airways and Acini}

% (cambiare `acini`) (paper in chat Lutchen). (no zsoft e
% cartilagine)

% Scrivere in breve la struttura circuitale che poi implemento
% (copia).

% La struttura circuitale è descritta in lutchen1997 in marrone.

The adult airway can be likened to a transmission line (see
\cref{fig:airway_impedance}), with resistors, capacitors and inductors
having constant values.  These components form a circuit as
illustrated.  Moreover, tissues properties ($Z_{\text{w}}$) are
incorporated.  \Cref{fig:airway_impedance,fig:acinus_impedance} are
modules connected according to the structure of newborn airway, which
is comparable to that depicted in
\Cref{fig:albero_dicotomico_anatomical}.  $Z(n)$ represents the parent
branch as a function of the Horsfield order, while $Z(n-1)$ and
$Z(n-1-\Delta)$ denote the two daughters branches.  $Z(2)$ represents
the terminal airway.  Each airway has a parent branch (excluding the
trachea) and two daughter branches (excluding the acini).

% L'equivalente elettrico delle proprietà dei tessuti è stato modificato
% per poter testare l'impatto delle modifiche fisiologiche durante il
% processo di aereazione.

The electrical equivalent of tissues properties is modified to test
the physiological change impact on aeration process.

% Inoltre, il liquido fetale è incomprimibile, l'aria invece non lo è,
% comportando la presenza di un elemento aggiuntivo nell'equivalente
% elettrico dell'aria, in quanto la compressibilità del gas è
% modellizzata attraverso una capacità. In aggiunta, bisogna tener conto
% del collasso delle vie aeree, perché durante il processo di aerazione
% si crea un'interfaccia aria-liquido, che a sua volta dà origine a una
% tensione superficiale, la quale deve essere superata per permettere lo
% spostamento del fluido nell'albero bronchiale.  Una volta superata, i
% diametri si possono ingrandire facendo aumentare il volume polmonare.

Air-fluid interface modulates the values of resistances and
inductances in both the modules types.

Moreover, this fluid is incompressible, whereas air is not. This
introduces an additional element in the electrical equivalent of air,
as the compressibility of the gas is modeled through a
capacitance.

% Additionally, it is necessary to consider the collapse of
% the airways.

During the aeration process, an air-liquid interface is created, which
in turn generates surface tension that must be overcome to allow fluid
movement within the bronchial tree. Once this surface tension is
overcome, the diameters can expand, leading to an increase in lung
volume.

\textcite{lutchen1997} have developed a mechanical lung model in
frequency-domain, describing airways and acini modules as displayed
in \cref{fig:airway_impedance} and \cref{fig:acinus_impedance},
respectively.

% Circuiti copiato da lutchen1997. 
\input{Images/equivalent_airway_impedance.tex}
\input{Images/equivalent_acinus_impedance.tex}

In this thesis, as well as in \cite{mani2020}, a mechanical model is
defined in time-domain starting from the modules described in this
section and properly adapted.

% AGGIUNTA MODIFICA, COMPLETARE
% -> la parte sul fluido è stata inserita sopra
% -> la parte del diodo è stata inserita sotto.

% In questo punto devo inserire la spiegazione del modello in cui si
% inserisce anche il diodo, oltre al liquido. proprio perché mani2020
% è stata la prima ad inserirlo.

% liquido .. diodo

Capillary pressure is due to air-fluid interface in the airway tree.
It was taken into account and modeled as a diode component: opening
threshold voltage is correspondent to aforementioned capillary
pressure for a generic airway.

% Da spostare in implementation? 
A first implementation has been performed on «CADENCE» platform.  This
has the advantage of parallelism and speed.  There are also some
drawbacks to this approach: this framework is designed to simulate
standard electrical components and it is not well-suited to develop
time- and current integral-dependent components.  Furthermore license
is proprietary and machine specific.  This limits the accessibility of
of model design process.

% Posso dire che l'alveolo è stato modificato (vedi Veneroni2024) a
% partire dall'alveolo mostrato da lutchen1997 perché non risolvibile
% nel dominio del tempo.

%%% Local Variables:
%%% mode: LaTeX
%%% TeX-master: "../Thesis"
%%% End:
