\section{Model Development}
\label{sec:model_development}

% model development: copio la prima parte o la summarizzo, prendo
% quello che serve per spiegare le figure e poco più.

%% ex Figure 3
\input{Images/pipeline_executive_v1}

An anatomically coherent 3D lung model is combined with a mechanical
model of the airways and acini, able to simulate changes in the
mechanical properties of the airways when the lung fluid is replaced
by air entering the lungs.

The sequence for model development is reported in
\cref{fig:data_pipeline}. We extracted a 3D surface mesh of lung lobes
and airway centrelines from a lung CT of a newborn.  Morphology
generation process is required as it is not possible to obtain high
generations (aka small airways) using standard high-resolution CT.

We implemented a statistical method, previously described for adult
lung models, able to generate distal airways that were not visible on
the CT\cite{bordas2015,tawhai2000}. We adapted the method for the
newborn lung.  This is performed by «Chaste», an open-source C++
library for computational physiology.  The «Chaste» User Project
required for airways and lobar segmentations to generate the distal
airways.

We implemented a mechanical model of the airways and acini whose
parameters are dependent on the airway's lengths and diameters and the
presence of fetal fluid, fetal fluid-air interface, or air in the
airway. We exploited an open-source solver for differential equations
to simulate the network.

To perform simulation it is required to use an efficient differential
equation solver.  Julia Programming Language\cite{juliadocs2024} has
«\texttt{DifferentialEquations.jl}»\cite{rackauckas2017}, which is
very efficient and includes all available solvers (even C and FORTRAN
ones)\cite{diffeqdocs2024,rackauckas2017}.
«\texttt{ModelingToolkit.jl}»\cite{ma2021} is also required: it is a
package for model design and instantiation.  It allows for prototyping
components easily, using macros and a Domain-Specific Language
optimized for such purpose.  Lung model is made out of modules at
various hierarchical levels: from the lowest ones at the level of the
electrical component to the highest ones emulating acini and airways
(see their schematics in \cref{fig:airway,fig:acinus}).

Simulations are executed starting from a subtree (see
\cref{fig:subtree_development}), as the full circuit (comprising over
50k modules) requires more memory space than typically available on a
common laptop.



%% ex Figure 4
\input{Images/equivalent_airway_executive}

%% ex Figure 5
\input{Images/equivalent_acinus_executive}

%% subtree
\input{Images/subtree_vertical_executive}

%%% Local Variables:
%%% mode: LaTeX
%%% TeX-master: "../Executive"
%%% End:
